%Document classification is a technique that algorithmically categorizes
%documents into a fixed set of categories.

In this term project, we aim to design and develop a document classification technique
that can complement the outcomes from the previous semesters.
Particularly, our design is focused on improving the following aspects, in
classifying the huge tweet collections into predefined categories.
First, the result of the classification should be reliable so they can be
practically utilized in decision makings.
To this end, we plan to achieve higher accuracy, by exploring and adopting the
state-of-the-art algorithms, than the previous classification techniques
provide.
In addition, an intelligent spam filtering technique will also be studied and developed.
Second, the classification system should perform in a scalable manner.
The amount of data that data analysis softwares need to ingest is
increasing unprecedentedly, and, therefore, it is crucial for such softwares to
provide deterministic and scalable performance for effectively supporting
decision making processes.
To achieve such scalability with respect to the increasing amount of the data,
our classification software will attentively orchestrate the I/O behaviors of
individual worker threads by considering the underlying system framework.

This interim report clarifies the problem that we address along with our
project goals, and summarizes related theories and practical techniques,
%including previous achievements in this course.
We then lastly provide our concrete execution plans.
%and lastly present our preliminary results.

